Preprocessing

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: refactor constants

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
# library(showtext)
# font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
```

@@

```{r word clouds}
cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
# saveRDS(clouds, file = "data/clouds.rds")
```

```{r q6 cloud}
subfields <- list("Human", "Methods", "Nature/society", "Physical")
types <- list("Quantitative", "Qualitative", "Mixed Methods")

clouds_q6_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q6", data = .)
) %>%
  set_names(subfields)

@@

```{r q5}

```

>>>>

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
library(showtext)
font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
source("data/constants.R")
```

@@

```{r word clouds}
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
# saveRDS(clouds, file = "data/clouds.rds")
```

```{r q6 cloud}
clouds_q6_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q6", data = .)
) %>%
  set_names(subfields)

@@

```{r q5}
analysis %>%
  mutate(Q5_num = as.numeric(four_levels[Q5])) %>%
  ggplot() +
  scale_x_continuous(
    breaks = as.numeric(four_levels),
    labels = str_wrap(names(four_levels), width = 9)
  ) +
  geom_density(aes(x = Q5_num), adjust = 1.6) +
  theme_minimal() +
  theme(
    text = element_text(family = "Fira Sans", size = 16),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(
    title = "How familiar are you with the term \"reproducibility\"?",
    subtitle = "In the context of conducting research",
    x = "", y = ""
  )
```
